Towards a standardized evaluation of multiple imputation routines

### 2022-03-04 Manuscript/StandardizedEvaluation.Rmd
Split up manuscript and simulation in separate markdown files

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
source(here::here("R/utils.R"))
source(here::here("R/run_sim.R"))
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
library(dplyr)
# source(here::here("R/utils.R"))
# source(here::here("R/run_sim.R"))
```

@@

# Structure

1. introduction

- aim
- number of simulations

2. data generation

- model vs design based
- data types
- sample vs population (vs bootstrapping??)
- number of observations
- number of variables
- coherence between variables

3. missingness generation

- monotone/univariate vs multivariate
- missingness mechanism
- type of M(N)AR
- missingness proportion (vs proportion of incomplete cases! 50% incomplete == 25% missing in bivariate data)

4. missing data methods

- imputation method
- number of imputations
- number of iterations

5. performance evaluation

- estimand
- diagnostic
- ppc
